Top antibiotic users

### 2017-03-28 top-users/top-users.Rmd
top users TB

- Merge amox, amox/clav
- Exclude TB drugs? Do with and without?
- Split people into top users (by # claims) or not
- Analyze them that way (with CPKP)
- Add zeros for people/drug combos? Or just find one denominator and pad out
- Then repeat the same thing but using days (and DID)
- Make plots & tables to compare both

Expected punchlines:

- TB drugs make up a lot of the top use
- Top claims enrich for vancomycin, which people are taking with ~2 day claims
- Top days are for mostly the same drugs

@@

```{r tb_drugs}
tb_drugs = c('isoniazid', 'rifabutin', 'rifampin', 'rifampin/isoniazid', 'rifampin/isoniazid/pyrazinamide', 'rifapentine', 'rifamixin', 'pyrazinamide', 'ethambutol')
stopifnot(all(tb_drugs %in% unique(pde$drug)))

@@

```{r compute_user_overlap}
# The idea here was to see about the overlap between drug users.
# If you took drug 1, how likely was it for you to also take drug 2?
# This is actually pretty similar to the tetrachoric analysis I did previously.
# Instead, I summarized the confusion matrix with the Matthews correlations coefficient.

drugs = pde$drug %>% unique

user_overlap = function(pde, drug1_name, drug2_name) {
  full_join(pde %>% filter(drug==drug1_name) %>% rename(drug1=drug),
            pde %>% filter(drug==drug2_name) %>% rename(drug2=drug), by='bene_id') %>%
    replace_na(list(drug1=0, drug2=0)) %>%
    mutate(case=case_when(.$drug1 > 0 & .$drug2 > 0 ~ 'took_both',
                          .$drug1 > 0 ~ 'took_drug1_only',
                          .$drug2 > 0 ~ 'took_drug2_only',
                          TRUE ~ 'took_neither')) %>%
    count(case) %>%
    spread(case, n) %>%
    mutate(drug1=drug1_name, drug2=drug2_name)
}

mcc = function (tp, fp, fn, tn) {
  # tp = true positive, fp = false positive, etc.
  n = as.double(tp + fp + fn + tn)
  s = (tp + fn) / n
  p = (tp + fp) / n
  return (tp / n - (s * p)) / sqrt(p * s * (1 - s) * (1 - p))
  #return ((tp * tn) - (fp * fn)) / sqrt((tp + fp) * (tp + fn) * (tn + fp) * (tn + fn))
}

#drug_overlap = crossing(drug1=drugs, drug2=drugs) %>%
#  filter(drug1 > drug2) %>%
#  rowwise() %>% do(user_overlap(pde, .$drug1, .$drug2)) %>%
#  mutate(took_neither=n_bene-(took_both + took_drug1_only + took_drug2_only)) %>%
#  select(drug1, drug2, took_both, took_drug1_only, took_drug2_only, took_neither) %>%
#  mutate(mcc=mcc(took_both, took_drug1_only, took_drug2_only, took_neither))
```

```{r top_user_overlap}
# The idea here was to ask which users are the "top" users for that drug.
# Then I would overlap them in the same way that I did for any-users above.

pad_to = function(x, n, with=0) {
  if (length(x) > n) stop('input longer than pad to length')
  c(x, rep(0, n - length(x)))
}

top_bracket_limit = function(n, fraction) {
  n[cume_dist(n) > (1 - fraction)] %>% min
}

#drug_upper_brackets = pde %>%
#  inner_join(pde %>% group_by(bene_id) %>% summarize(n_claims=sum(n_claims)) %>% mutate(antibiotic='all'), by='bene_id') %>%
#  group_by(antibiotic) %>%
#  summarize(limit=top_bracket_limit(pad_to(n_claims, n_bene), 0.001)) %>%
#  filter(limit > 0)
```

>>>>

@@

```{r tb_drugs}
tb_drugs = c('isoniazid', 'rifabutin', 'rifampin', 'rifampin/isoniazid', 'rifampin/isoniazid/pyrazinamide', 'rifapentine', 'rifaximin', 'pyrazinamide', 'ethambutol')
stopifnot(all(tb_drugs %in% unique(pde$drug)))

@@

`r top_notb_table`

The results don't seem like they change that much.
